---
title: "OU_sim_fit"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(PCMBase)
library(ape)
library(magrittr)
library(matrixcalc)
#library(Matrix) 
library(ggtree)
library(plotly)
#library(r)
source("tool_funs.R")
```

```{r}
#save.image(file = "Rda/sym_tp1_v1.RData") # tree test hitree=2
 
```



# 1 Model's Building and Simulation


##  1.1 Setting trait dimenstion k, tips N, root X0, tree, builing model and simulation----------------------------
```{r}
#set.seed(12345)
#source("tool_funs.R")
#-------------------------------------------------------------------------------
model_type="OU"  
Htype=1   # real sym with real eigenvalue of H
k=2
N <-100 # tips
X0<-runif(k,-1,1)
tree <- PCMTree(rtopology(n=N,rooted = TRUE))  # topology and branch length
#save.image(file = "Rda/tree_p_0423.RData")
#-------------------------------------------------------------------------------

Theta =runif(k,-3,3)
#-------------------------------------------------------------------------------
egv_Sigma2_x = runif(k,0.1,0.3)%>%sort(decreasing = TRUE) 
Q_sigma = Gen_Q(k)
Sigma2_x = Gen_Sigma2(egv_Sigma2_x,Q_sigma,k)
Sigma_x<-my_chol(Sigma2_x)
#------------------------------------
P = Gen_Q(k)

#tree <- PCMTree(rtree(n=N,rooted = TRUE))
```


here
```{r}
#load("D:/DataScience/LiuCourses/masterThesis/TheFormalCode/Rdata/TX0_symH_02_2d.RData")
#save.image(file = "Rdata1/tree2d_0416.RData")# egv_H = c(1.9, 1.6, 1.1) v1 v2
```

## 1.2 setting the cases of eigen values of H and generating data

```{r}
#-------------------------------------------
egv_1st_H<-3
egv_2nd_H<-c(3,1.5,-0.5,-0.75,-0.8,-0.9,-0.925,-0.95,-1,-1.25,-1.5,-2,-3,-3.5,-4,-5)  #c(seq(from = egv_1st_H+0.1, to = 0.1,by=-0.1)[-c(1)],seq(from = 0, to = -1,by=-0.05)[-c(1)],c(-1.25,-1.5,-1.75,-2,-3))
egv_H_lst<-lapply(egv_2nd_H, function(x)c(egv_1st_H,x)) 

#--------------------------------------------------------------------------------------------------------------
Gen_OU<-function(k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma){
  
  H = Gen_H(egv_H,k,P)
  Sigma2_x = Gen_Sigma2(egv_Sigma2_x,Q_sigma,k)
  Sigma_x<-my_chol(Sigma2_x)
  #--------------------------------------------------------------------------------------------------------------
  model_MOU <- PCM(model = model_type , k = k) #OUC (diagonal H, diagonal Σ): OU, uncorrelated traits;

  model_MOU$X0[] = X0#%>%as.vector()
  model_MOU$Theta[] = Theta
  model_MOU$H[] = H
  model_MOU$Sigma_x[] = Sigma_x
  #model_MOU$Sigmae_x[] = Sigmae_x

  return(model_MOU)
}

model_MOU_lst<-lapply(egv_H_lst, function(egv_H)Gen_OU(k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma))
  


#-----------------------------------------------------------------------------------------------------------------
Gen_Traits<-function(tree,model_MOU){
  # equal prob for each topology
  traits <- PCMSim(tree, model_MOU, model_MOU$X0)#[,tree$tip.label]
  traits<-traits[,tree$tip.label]
  
  return(traits)
}

traits_lst<-lapply(model_MOU_lst, function(model_MOU)Gen_Traits(tree,model_MOU))
  
  
#traits
###################################
cmp_lf_mou<-function(tree,k,model_MOU,traits){
  
  
 #model_trait<-Gen_Traits(tree,k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma)
 #model_MOU<-model_trait$model
# traits <- model_trait$traits
  
  param <- double( PCMParamCount(model_MOU) )
  PCMParamLoadOrStore(model_MOU, param, offset=0, load=FALSE)
  likFun <- PCMCreateLikelihood(traits, tree, model_MOU)
  
  return(list(lik=likFun(param)[1],param=param,model=model_MOU))
}

cnt_H<-length(egv_2nd_H) 

r_lm_lst<-list()
for(i in c(1:cnt_H)){
  r_lm_lst[[i]]<-cmp_lf_mou(tree,k,model_MOU_lst[[i]],traits_lst[[i]])
}
#r_lm_lst
```







# 2 Experiment 

## 2.1 eigenvalue of H

### 1) Trying different eigenvalues

1.1 observing the trend in raw way, finding the transitioning zone
```{r}
#t_dim=1
test_egv_H_llk<-function(t_dim){
  print(paste0(H_i,":"))
  print(egv_H_lst[[H_i]])
  print(paste0("k=",t_dim))
  egv_H_arr[,,t_dim]
  egv_H_lst_p<-lapply(c(1:n_t), function(i)egv_H_arr[i,,t_dim])
  llk<-lapply(egv_H_lst_p, function(egv_H)cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma),traits_lst[[H_i]])$lik )%>%unlist()
  
  plot_ly(x =egv_H_arr[,t_dim,t_dim], y =llk, type = 'scatter', name="lik test",mode = 'markers') %>%   # mode = 'lines',
    add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0",t_dim))%>%
    add_lines(x=egv_H_lst[[H_i]][t_dim],name=paste0("lambda_",t_dim))
  }

n_t=33

t=Sys.time()
p_H_egv<-list()
##############################
#H_i=25
for(H_i in c(7:10)){

  egv_H_arr<-array(0, dim = c(n_t, k, k))
lambda_i=seq(-6,6,length.out=n_t)
for(t_dim in 1:k){
  egv_H_arr[,,t_dim][,t_dim] = lambda_i
  egv_H_arr[,,t_dim][,-c(t_dim)]  = rep(egv_H_lst[[H_i]][-c(t_dim)],n_t)%>%matrix(byrow = TRUE,nrow = n_t)
    
  }
  
#for(t_dim in 1:k)
 pegvh<-list()
 for(i in c(1:k))pegvh[[i]]<-test_egv_H_llk(t_dim=i)
 
 p_H_egv[[H_i]]<-subplot(pegvh)
}
Sys.time()-t


p_H_egv_1<-p_H_egv
cnt_H
p_H_egv_1
#for(i in c(1,3,18,19,20,21,cnt_H))print(p_H_egv_1[[i]])

#c_sel<-c(1,2,18,19,20,21)
# 19,20,21

#c_sel<-c(1,2,20,21,35,46)  #0416-sys

#egv_H_lst[c_sel]
#egv_H_lst[c(20:cnt_H)]

egv_H_lst[c(8:10)]
```

```{r}
#t_dim=1
test_egv_H_llk<-function(t_dim){
  print(paste0(H_i,":"))
  print(egv_H_lst[[H_i]])
  print(paste0("k=",t_dim))
  egv_H_arr[,,t_dim]
  egv_H_lst_p<-lapply(c(1:n_t), function(i)egv_H_arr[i,,t_dim])
  llk<-lapply(egv_H_lst_p, function(egv_H)cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma),traits_lst[[H_i]])$lik )%>%unlist()
  
  plot_ly(x =egv_H_arr[,t_dim,t_dim], y =llk, type = 'scatter', name="Experiment Likelihood",mode = 'markers') %>%   # mode = 'lines',
    add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("Data Likelihood"))#%>%
    #add_lines(x=egv_H_lst[[H_i]][t_dim],name=paste0("True Eigenvalue in the Dimension"))
  }

n_t=333

t=Sys.time()
p_H_egv<-list()
##############################
#H_i=25
for(H_i in c(1,2,3,8:10
             )){

  egv_H_arr<-array(0, dim = c(n_t, k, k))
lambda_i=seq(-6,6,length.out=n_t)
for(t_dim in 1:k){
  egv_H_arr[,,t_dim][,t_dim] = lambda_i
  egv_H_arr[,,t_dim][,-c(t_dim)]  = rep(egv_H_lst[[H_i]][-c(t_dim)],n_t)%>%matrix(byrow = TRUE,nrow = n_t)
    
  }
  
#for(t_dim in 1:k)
 pegvh<-list()
 for(i in c(1:k))pegvh[[i]]<-test_egv_H_llk(t_dim=i)
 
 p_H_egv[[H_i]]<-pegvh #subplot(pegvh)
}
Sys.time()-t


p_H_egv_1<-p_H_egv
cnt_H
p_H_egv_1
#for(i in c(1,3,18,19,20,21,cnt_H))print(p_H_egv_1[[i]])

#c_sel<-c(1,2,18,19,20,21)
# 19,20,21

#c_sel<-c(1,2,20,21,35,46)  #0416-sys

#egv_H_lst[c_sel]
#egv_H_lst[c(20:cnt_H)]

egv_H_lst#[c(6:10)]

 p_H_egv_1[[3]][[1]] %>% layout(title =  TeX("\\textbf{Likelihood vs Experiment Eigenvalues in the First Dimension of } \\mathbf H"),
         xaxis = list(title = TeX("\\textbf{Experiment Eigenvalues}")
                      
                     ),
         yaxis = list(title = TeX("\\textbf{Likelihood}")
                     )) %>% config(mathjax = 'cdn')
 
 
p_H_egv_1[[8]][[2]] %>% layout(title = 'Likelihood vs Experiment Eigenvalues of Second Dimension',
       xaxis = list(title = 'Experiment Eigenvalues'
                    
                   ),
       yaxis = list(title = 'Likelihood'
                   ))



subplot(p_H_egv_1[[2]][[1]],p_H_egv_1[[8]][[1]],p_H_egv_1[[10]][[1]])

```




2)  careful observing the trend on the selected data sets,
```{r}
#t_dim=1
test_egv_H_llk<-function(t_dim){
  egv_H_arr[,,t_dim]
  egv_H_lst_p<-lapply(c(1:n_t), function(i)egv_H_arr[i,,t_dim])
  llk<-lapply(egv_H_lst_p, function(egv_H)cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma),traits_lst[[H_i]])$lik )%>%unlist()
  
  plot_ly(x =egv_H_arr[,t_dim,t_dim], y =llk, type = 'scatter', name="lik test",mode = 'markers') %>%   # mode = 'lines',
    add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0",t_dim))%>%
    add_lines(x=egv_H_lst[[H_i]][t_dim],name=paste0("lambda_",t_dim))
  }

n_t=300

t=Sys.time()
p_H_egv<-list()
##############################
#H_i=25
for(H_i in c_sel){
  egv_H_arr<-array(0, dim = c(n_t, k, k))
lambda_i=seq(-3,3,length.out=n_t)
for(t_dim in 1:k){
  egv_H_arr[,,t_dim][,t_dim] = lambda_i
  egv_H_arr[,,t_dim][,-c(t_dim)]  = rep(egv_H_lst[[H_i]][-c(t_dim)],n_t)%>%matrix(byrow = TRUE,nrow = n_t)
    
  }
  
#for(t_dim in 1:k)
 pegvh<-list()
 for(i in c(1:k))pegvh[[i]]<-test_egv_H_llk(t_dim=i)
 
 p_H_egv[[H_i]]<-subplot(pegvh)
}
Sys.time()-t


p_H_egv_2<-p_H_egv
cnt_H

#for(i in c(1,3,18,19,20,21,cnt_H))print(p_H_egv_1[[i]])

```







### 2.2  multiplication by a rotation/unitary matrix  P*R 

```{r}
 # rotation in one plane
ang=pi/2
#k=2
k1=1
k2=2
rotate_cmp<-function(ang,k,k1,k2){
  r_mx<-diag(1,k)
  rt<-matrix(c(cos(ang),sin(ang),-sin(ang),cos(ang)),nrow = 2  ) 
  r_mx[k1,c(k1,k2)]<- rt[1,]
  r_mx[k2,c(k1,k2)]<- rt[2,]
  
  return(r_mx)
  }    

rotate_cmp(ang,k,k1,k2)

```



```{r}
n_t=333
ang_lst<-seq(0,2*pi,length.out=n_t)[-c(1,n_t)]

P_rt_lst<-lapply(ang_lst,function(ang)rotate_cmp(ang,k,k1,k2)%*%P )


rt_pl_lst<-list()  # rt_pl_lst[[]]
m<-1
for(i in c(1:(k-1))){
  for(j in c((i+1):k)){
    rt_pl_lst[[m]]<-c(i,j)
    m=m+1
  }
  
}

test_egv_P_rt_llk<-function(ang_lst,rt_pl){
 # egv_H_arr[,,t_dim]
 # egv_P_lst<-lapply(p_r_v, function(r)r*P)
  k1=rt_pl[1]
  k2=rt_pl[2]
  P_rt_lst<-lapply(ang_lst,function(ang)P%*%rotate_cmp(ang,k,k1,k2) )
  print(paste0(H_i,":"))
  print(egv_H_lst[[H_i]])
  llk<-lapply(P_rt_lst, function(P)cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H_lst[[H_i]],P,Theta,egv_Sigma2_x,Q_sigma),traits_lst[[H_i]])$lik )%>%unlist()
  
  p<-plot_ly(x =ang_lst, y =llk, type = 'scatter', name="lik test",mode = 'markers') %>%   # mode = 'lines',
    add_lines( y=r_lm_lst[[H_i]]$lik,name='lik0')
  #llk
  
  return(list(llk=llk,p=p))
  }

p_rt_lst<-list()
p_rt_lst_llk<-list()
for(H_i in c(1:cnt_H) ){
  res<-test_egv_P_rt_llk(ang_lst,c(1,2))
  p_rt_lst[[H_i]]<-res$p #(lapply(rt_pl_lst,function(rt_pl)test_egv_P_rt_llk(ang_lst,rt_pl))  )  %>%subplot()
   p_rt_lst_llk[[H_i]]<-res$llk
}

p_rt_lst




#res_tb1_p_rt<-list()
#res_tb2<-list()
#for(ix in c(1:cnt_H) ){
#  res_tb1_p_rt[[ix]]<-table((p_rt_lst_llk[c_sel[ix]][[1]]- r_lm_lst[c_sel[ix]][[1]]$lik)>0)
 # res_tb2[[ix]]<-table((tr12_2_lik_lst[c_sel_al[ix]][[1]]- r_lm_lst[c_sel_al[ix]][[1]]$lik)>0)
  
#}

 p_rt_lst[[1]] %>% layout(title =  TeX("\\textbf{Likelihood vs Experiment Eigenvalues in the First Dimension of } \\mathbf H"),
         xaxis = list(title = TeX("\\textbf{Angle of Rotation Matrix}")
                      
                     ),
         yaxis = list(title = TeX("\\textbf{Likelihood}")
                     )) %>% config(mathjax = 'cdn')


```




## 2.3 Theta


### 1) Trying differnet Theta values
```{r}

n_t=33#0

Theta_arr<-array(0, dim = c(n_t, k, k))
Theta_i=seq(-10,10,length.out=n_t)
for(t_dim in 1:k){
  Theta_arr[,,t_dim][,t_dim] = Theta_i
  Theta_arr[,,t_dim][,-c(t_dim)]  = rep(Theta[-c(t_dim)],n_t)%>%matrix(byrow = TRUE,nrow = n_t)
    
  }
  

#cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma),traits)$lik
#cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H=runif(k),P,Theta,egv_Sigma2_x,Q_sigma),traits)$lik


#t_dim=1
test_Theta_llk<-function(t_dim){
 # egv_H_arr[,,t_dim]
   print(paste0(H_i,":"))
  print(egv_H_lst[[H_i]])
  print(paste0("k=",t_dim))
  Theta_lst<-lapply(c(1:n_t), function(i)Theta_arr[i,,t_dim])
  llk<-lapply(Theta_lst, function(Theta)cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H_lst[[H_i]],P,Theta,egv_Sigma2_x,Q_sigma),traits_lst[[H_i]])$lik )%>%unlist()
  
  plot_ly(x =Theta_arr[,t_dim,t_dim], y =llk, type = 'scatter', mode = 'markers',name=paste0("Theta",t_dim))%>%
    add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0")) %>% #add_segments( x=-6,xend=6, y = r_lm$lik, yend = r_lm$lik,name='lik0')
    add_lines(x=Theta[t_dim],showlegend = FALSE)
  #llk
  }

pTheta_lst1<-list()
for(H_i in c(1:cnt_H)  ){ #
  pTheta<-list()
  for(i in c(1:k))pTheta[[i]]<-test_Theta_llk(t_dim=i)
pTheta_lst1[[H_i]]<-subplot(pTheta)
}

#pTheta_lst[[22]]
#H_i=28

#c_sel_tta<-c(1,2,21,22,23,24,42,46)

```


careful checking
```{r}

n_t=300

Theta_arr<-array(0, dim = c(n_t, k, k))
Theta_i=seq(-10,10,length.out=n_t)
for(t_dim in 1:k){
  Theta_arr[,,t_dim][,t_dim] = Theta_i
  Theta_arr[,,t_dim][,-c(t_dim)]  = rep(Theta[-c(t_dim)],n_t)%>%matrix(byrow = TRUE,nrow = n_t)
    
  }
  

#cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma),traits)$lik
#cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H=runif(k),P,Theta,egv_Sigma2_x,Q_sigma),traits)$lik


#t_dim=1
test_Theta_llk<-function(t_dim){
 # egv_H_arr[,,t_dim]
   print(paste0(H_i,":"))
  print(egv_H_lst[[H_i]])
  print(paste0("k=",t_dim))
  Theta_lst<-lapply(c(1:n_t), function(i)Theta_arr[i,,t_dim])
  llk<-lapply(Theta_lst, function(Theta)cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H_lst[[H_i]],P,Theta,egv_Sigma2_x,Q_sigma),traits_lst[[H_i]])$lik )%>%unlist()
  
  p<-plot_ly(x =Theta_arr[,t_dim,t_dim], y =llk, type = 'scatter', mode = 'markers',name=paste0("Theta",t_dim))%>%
    add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0")) %>% #add_segments( x=-6,xend=6, y = r_lm$lik, yend = r_lm$lik,name='lik0')
    add_lines(x=Theta[t_dim],showlegend = FALSE)
  #llk
  
  return(list(p=p,llk=llk))
  }

pTheta_lst2_llk<-list()
pTheta_lst2<-list()
for(H_i in c_sel_tta  ){ #
  pTheta<-list()
  for(i in c(1:k))pTheta[[i]]<-test_Theta_llk(t_dim=i)
  pTheta_lst2[[H_i]]<-subplot(pTheta)
}

#pTheta_lst[[22]]
#H_i=28

#c_sel_tta<-c(1,2,21,22,23,24,42,46)

```







## 2.4 eigenvalue of Sigma

### 1) trying different eigenvlues 

```{r}

n_t=30#0

egv_Sigma2_x_arr<-array(0, dim = c(n_t, k, k))
egv_Sigma2_x_i=seq(0.0000001,6,length.out=n_t)
for(t_dim in 1:k){
  egv_Sigma2_x_arr[,,t_dim][,t_dim] = egv_Sigma2_x_i
  egv_Sigma2_x_arr[,,t_dim][,-c(t_dim)]  = rep(egv_Sigma2_x[-c(t_dim)],n_t)%>%matrix(byrow = TRUE,nrow = n_t)
    
  }
  

#cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma),traits)$lik
#cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H=runif(k),P,Theta,egv_Sigma2_x,Q_sigma),traits)$lik


#t_dim=1
test_egv_Sigma2_x_llk<-function(t_dim){
 # egv_H_arr[,,t_dim]
  
  print(paste0(H_i,":"))
  print(egv_H_lst[[H_i]])
  print(paste0("k=",t_dim))
  egv_Sigma2_x_lst<-lapply(c(1:n_t), function(i)egv_Sigma2_x_arr[i,,t_dim])
  llk<-lapply(egv_Sigma2_x_lst, function(egv_Sigma2_x)cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H_lst[[H_i]],P,Theta,egv_Sigma2_x,Q_sigma),traits_lst[[H_i]])$lik )%>%unlist()
  
  plot_ly(x =egv_Sigma2_x_arr[,t_dim,t_dim], y =llk, type = 'scatter',  mode = 'markers',name=paste0("Sigma2_",t_dim))%>%
    add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0")) %>% #add_segments( x=-6,xend=6, y = r_lm$lik, yend = r_lm$lik,name='lik0')
    add_lines(x=egv_Sigma2_x[t_dim],showlegend = FALSE)
  #llk
  }


#c_sel_al<-c(c_sel,c_sel_tta)%>%unique()%>%sort()

pegv_Sigma2_x_lst<-list()
for(H_i in c(1:cnt_H)   ){
  pegv_Sigma2_x<-list()
  for(i in c(1:k)){ pegv_Sigma2_x[[i]]<-test_egv_Sigma2_x_llk(t_dim=i)}
  pegv_Sigma2_x_lst[[H_i]]<-(pegv_Sigma2_x%>%subplot())
}

pegv_Sigma2_x_lst


```




```{r}

n_t=333 #0

egv_Sigma2_x_arr<-array(0, dim = c(n_t, k, k))
egv_Sigma2_x_i=seq(0.0000001,3,length.out=n_t)
for(t_dim in 1:k){
  egv_Sigma2_x_arr[,,t_dim][,t_dim] = egv_Sigma2_x_i
  egv_Sigma2_x_arr[,,t_dim][,-c(t_dim)]  = rep(egv_Sigma2_x[-c(t_dim)],n_t)%>%matrix(byrow = TRUE,nrow = n_t)
    
  }
  

#cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H,P,Theta,egv_Sigma2_x,Q_sigma),traits)$lik
#cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H=runif(k),P,Theta,egv_Sigma2_x,Q_sigma),traits)$lik


#t_dim=1
test_egv_Sigma2_x_llk<-function(t_dim){
 # egv_H_arr[,,t_dim]
  
  print(paste0(H_i,":"))
  print(egv_H_lst[[H_i]])
  print(paste0("k=",t_dim))
  egv_Sigma2_x_lst<-lapply(c(1:n_t), function(i)egv_Sigma2_x_arr[i,,t_dim])
  llk<-lapply(egv_Sigma2_x_lst, function(egv_Sigma2_x)cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H_lst[[H_i]],P,Theta,egv_Sigma2_x,Q_sigma),traits_lst[[H_i]])$lik )%>%unlist()
  
  plot_ly(x =egv_Sigma2_x_arr[,t_dim,t_dim], y =llk, type = 'scatter',  mode = 'markers',name=paste0("Sigma2_",t_dim))%>%
    add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0")) %>% #add_segments( x=-6,xend=6, y = r_lm$lik, yend = r_lm$lik,name='lik0')
    add_lines(x=egv_Sigma2_x[t_dim],showlegend = FALSE)
  #llk
  }


#c_sel_al<-c(c_sel,c_sel_tta)%>%unique()%>%sort()

pegv_Sigma2_x_lst<-list()
for(H_i in c(1,2,3,8,9,10)   ){
  pegv_Sigma2_x<-list()
  for(i in c(1:k)){ pegv_Sigma2_x[[i]]<-test_egv_Sigma2_x_llk(t_dim=i)}
  pegv_Sigma2_x_lst[[H_i]]<-(pegv_Sigma2_x%>%subplot())
}

pegv_Sigma2_x_lst


```






## 2.5 eigenvector of Sigma



### multiplication by a rotation/unitary matrix  P*R 

```{r}
n_t=333
ang_lst<-seq(0,2*pi,length.out=n_t)[-c(1,n_t)]

qs_rt_lst<-lapply(ang_lst,function(ang)rotate_cmp(ang,k,k1,k2)%*%P )


rt_pl_lst<-list()  # rt_pl_lst[[]]
m<-1
for(i in c(1:(k-1))){
  for(j in c((i+1):k)){
    rt_pl_lst[[m]]<-c(i,j)
    m=m+1
  }
  
}

test_egv_qs_rt_llk<-function(ang_lst,rt_pl){
 # egv_H_arr[,,t_dim]
 # egv_P_lst<-lapply(p_r_v, function(r)r*P)
  k1=rt_pl[1]
  k2=rt_pl[2]
  qs_rt_lst<-lapply(ang_lst,function(ang)Q_sigma%*%rotate_cmp(ang,k,k1,k2) )
  print(paste0(H_i,":"))
  print(egv_H_lst[[H_i]])
  llk<-lapply(qs_rt_lst, function(Q_sigma)cmp_lf_mou(tree,k,Gen_OU(k,X0,Htype,egv_H_lst[[H_i]],P,Theta,egv_Sigma2_x,Q_sigma),traits_lst[[H_i]])$lik )%>%unlist()
  
  plot_ly(x =ang_lst, y =llk, type = 'scatter', name="lik test",mode = 'markers') %>%   # mode = 'lines',
    add_lines( y=r_lm_lst[[H_i]]$lik,name='lik0')
  #llk
  }

qs_rt_lst<-list()
for(H_i in c(1:cnt_H) ){
  qs_rt_lst[[H_i]]<-(lapply(rt_pl_lst,function(rt_pl)test_egv_qs_rt_llk(ang_lst,rt_pl))%>%subplot()  )  
}



qs_rt_lst
```



## 2.6 Length/Edge, t

t, information propagating effect

```{r}
edge=data.frame(tree$edge, tree$edge.length)
colnames(edge)=c("parent", "node", "edge_length")
PCMTreeSetLabels(tree)  
#p<-ggtree(tree)+ geom_nodelab(size = 4)+geom_rootedge(rootedge = 0.1)+geom_tiplab()
#p %<+% edge + geom_label(aes(x=branch, label=edge_length))
PCMTreePlot(tree) + ggtree::geom_nodelab(size = 2)


```


```{r}

library(castor)
hitree=H_i
model_MOU=model_MOU_lst[[hitree]]
traits=traits_lst[[hitree]]
cmp_lf_mou(tree,k,model_MOU,traits)$lik
find_root(tree)
node.depth.edgelength(tree) %>%max()

#node.depth.edgelength(tree)%>%sum()


tree$edge.lengt%>%sum()
tree$edge.length[tree$edge[,2] %in% c(1:100)]%>%sum()
tree$edge.length[!(tree$edge[,2] %in% c(1:100))]%>%sum()
tree$edge.length[tree$edge[,2] %in% c(1:100)]%>%sum()+tree$edge.length[!(tree$edge[,2] %in% c(1:100))]%>%sum()

```



### 1)
```{r}
#tree_1$tip.label
#tree_1$edge.length
tree_mdf_1<-function(tree,N,t_r){  # reduce tip2parent, increase shared length, keep the sum of edge-length unchanged
  tree_1<-tree
  #tips_egde<-tree_1$edge[tree_1$edge[,2] %in% c(1:100),]
  t_dif<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]*t_r
  tips_edge_length<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]
  tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]<-tips_edge_length-t_dif
  nontips_edge_length<-tree_1$edge.length[!tree_1$edge[,2] %in% c(1:N)]
  tree_1$edge.length[!tree_1$edge[,2] %in% c(1:N)]<-nontips_edge_length+sum(t_dif)/length(nontips_edge_length)
  
  return(tree_1)
  
}

tree_mdf_2<-function(tree,N,t_r){  # increase tip2parent, reduce shared length
  tree_1<-tree
  #tips_egde<-tree_1$edge[tree_1$edge[,2] %in% c(1:100),]
  
  t_dif<-tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]*t_r
  nontips_edge_length<-tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]
  tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]<-nontips_edge_length-t_dif
 
  tips_edge_length<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]
  tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]<-tips_edge_length+sum(t_dif)/length(tips_edge_length)
  
   return(tree_1)
  
}


t_r<-0.1

tree_1<-tree_mdf_1(tree,N,t_r)
tree_2<-tree_mdf_2(tree,N,t_r)


tree_1$edge.lengt%>%sum()
tree_2$edge.lengt%>%sum()
#cmp_lf_mou(tree_1,k,model_MOU,traits)$lik
#cmp_lf_mou(tree_2,k,model_MOU,traits)$lik



```


```{r}

#plot(tr1_lik)
#plot(tr2_lik)
# likelihood of decreased shared length

t_r_lst<-seq(0,0.97,by=0.005)


tr_12<-function(H_i){
print(paste(":",H_i))
tr1_lik<-lapply(t_r_lst,function(t_r)cmp_lf_mou(tree_mdf_1(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()
tr2_lik<-lapply(t_r_lst,function(t_r)cmp_lf_mou(tree_mdf_2(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()
plik_1<-plot_ly(x =t_r_lst, y =tr1_lik, name = "tr1_lik",type = 'scatter',mode = 'markers')%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

plik_2<-plot_ly(x =t_r_lst, y =tr2_lik, name = "tr2_lik", type = 'scatter',mode = 'markers'   )%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

p<-subplot(plik_1, plik_2)

return(list(p=p,tr1_lik=tr1_lik,tr2_lik=tr2_lik))
}


res_tr_12_lst<-list()
tr12_1_lik_lst<-list()
tr12_2_lik_lst<-list()
for(H_i in c(1:cnt_H)   ){
  res<-tr_12(H_i)
  res_tr_12_lst[[H_i]] <-res$p
  tr12_1_lik_lst[[H_i]] <-res$tr1_lik
  tr12_2_lik_lst[[H_i]] <-res$tr2_lik
}

#res_tr_12_lst




c_sel_al1=c(1:cnt_H)
res_tb1<-list()
res_tb2<-list()
for(ix in c(1:length(c_sel_al1)) ){
  res_tb1[[ix]]<-table( (tr12_1_lik_lst[c_sel_al1[ix]][[1]]- r_lm_lst[c_sel_al1[ix]][[1]]$lik)>0 )
  res_tb2[[ix]]<-table( (tr12_2_lik_lst[c_sel_al1[ix]][[1]]- r_lm_lst[c_sel_al1[ix]][[1]]$lik)>0 )
  
}



ll<-length(t_r_lst)

res_tb1_td<-list()
res_tb2_td<-list()
for(ix in c(1:length(c_sel_al1)) ){
  res_tb1_td[[ix]]<-table((tr12_1_lik_lst[c_sel_al1[ix]][[1]][c(2:ll)]- tr12_1_lik_lst[c_sel_al1[ix]][[1]][c(1:(ll-1))])>0)
  res_tb2_td[[ix]]<-table((tr12_2_lik_lst[c_sel_al1[ix]][[1]][c(2:ll)]- tr12_2_lik_lst[c_sel_al1[ix]][[1]][c(1:(ll-1))])>0)
  
}


#plik_10<-plot_ly(x =t_r_lst[1:20], y =tr1_lik[1:20], name = "tr1_lik",type = 'scatter',mode = 'markers')

#plik_20<-plot_ly(x =t_r_lst[1:20], y =tr2_lik[1:20], name = "tr1_lik",type = 'scatter',mode = 'markers' )
#subplot(plik_10, plik_20)

#(tr1_lik[2:(length(t_r_lst))]-tr1_lik[1:(length(t_r_lst)-1)])>0







```

```{r}


tr_12_ett<-function(H_i){
print(paste(":",H_i))
tr1_lik<-lapply(t_r_lst,function(t_r)cmp_lf_mou(tree_mdf_1(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()
tr2_lik<-lapply(t_r_lst,function(t_r)cmp_lf_mou(tree_mdf_2(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()
plik_1<-plot_ly(x =t_r_lst, y =tr1_lik, name = "tr1_lik",type = 'scatter',mode = 'markers')%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

plik_2<-plot_ly(x =t_r_lst, y =tr2_lik, name = "tr2_lik", type = 'scatter',mode = 'markers'   )%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

#p<-subplot(plik_1, plik_2)

return(list(p1=plik_1,p2=plik_2))
}


rres<-tr_12_ett(H_i=2)





rres$p1 %>% layout(title =  TeX("\\textbf{Likelihood vs Experiment Eigenvalues in the First Dimension of } \\mathbf H"),
         xaxis = list(title = TeX("\\textbf{Increasing Rate of } t_{shr}")
                      
                     ),
         yaxis = list(title = TeX("\\textbf{Likelihood}")
                     )) %>% config(mathjax = 'cdn')


```




(c) Only decreasing  tpar or tshr


```{r}

#tree_1$tip.label
#tree_1$edge.length
tree_mdf_1e<-function(tree,N,t_r){  # only decrease t_par
  tree_1<-tree
  #tips_egde<-tree_1$edge[tree_1$edge[,2] %in% c(1:100),]
  t_dif<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]*t_r
  tips_edge_length<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]
  tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]<-tips_edge_length-t_dif
 # nontips_edge_length<-tree_1$edge.length[!tree_1$edge[,2] %in% c(1:N)]
 # tree_1$edge.length[!tree_1$edge[,2] %in% c(1:N)]<-nontips_edge_length+sum(t_dif)/length(nontips_edge_length)
  
  return(tree_1)
}

tree_mdf_2e<-function(tree,N,t_r){  # only decrease t_shr
  tree_1<-tree
  #tips_egde<-tree_1$edge[tree_1$edge[,2] %in% c(1:100),]
  
  t_dif<-tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]*t_r
  nontips_edge_length<-tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]
  tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]<-nontips_edge_length-t_dif
 
 # tips_edge_length<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]
#  tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]<-tips_edge_length+sum(t_dif)/length(tips_edge_length)
  
   return(tree_1)
}

```


```{r}
#t_r_lst<-seq(0,0.97,by=0.005)


tr_34<-function(H_i){
print(paste(":",H_i))  
tr1_like<-lapply(t_r_lst,function(t_r)cmp_lf_mou(tree_mdf_1e(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()
tr2_like<-lapply(t_r_lst,function(t_r)cmp_lf_mou(tree_mdf_2e(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()

plik_1e<-plot_ly(x =t_r_lst, y =tr1_like, name = "tr1_like",type = 'scatter',mode = 'markers')%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

plik_2e<-plot_ly(x =t_r_lst, y =tr2_like, name = "tr2_like", type = 'scatter',mode = 'markers')%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

p<-subplot(plik_1e, plik_2e)

return(list(p=p,tr1_like=tr1_like,tr2_like=tr2_like))
  
}




res_tr_34_lst<-list()
tr34_1_lik_lst<-list()
tr34_2_lik_lst<-list()
for(H_i in c(1:cnt_H)   ){
  res<-tr_34(H_i)
  res_tr_34_lst[[H_i]] <-res$p
  tr34_1_lik_lst[[H_i]] <-res$tr1_like
  tr34_2_lik_lst[[H_i]] <-res$tr2_like
}




res_tb1_34<-list()
res_tb2_34<-list()
for(ix in c(1:length(c_sel_al1)) ){
  res_tb1_34[[ix]]<-table((tr34_1_lik_lst[c_sel_al1[ix]][[1]]- r_lm_lst[c_sel_al1[ix]][[1]]$lik)>0)
  res_tb2_34[[ix]]<-table( (tr34_2_lik_lst[c_sel_al1[ix]][[1]]- r_lm_lst[c_sel_al1[ix]][[1]]$lik)>0 )
  
}


ll<-length(t_r_lst)

res_tb1_td_34<-list()
res_tb2_td_34<-list()
for(ix in c(1:length(c_sel_al1)) ){
  res_tb1_td_34[[ix]]<-table((tr34_1_lik_lst[c_sel_al1[ix]][[1]][c(2:ll)]- tr34_1_lik_lst[c_sel_al1[ix]][[1]][c(1:(ll-1))])>0)
  res_tb2_td_34[[ix]]<-table((tr34_2_lik_lst[c_sel_al1[ix]][[1]][c(2:ll)]- tr34_2_lik_lst[c_sel_al1[ix]][[1]][c(1:(ll-1))])>0)
  
}


#res_tr_34_lst<-list()
#for(H_i in c_sel_al   ){
#  res_tr_34_lst[[H_i]] <-tr_34(H_i)
#}

#res_tr_34_lst



#tr1_like[2:(length(t_r_lst))]-tr1_like[1:(length(t_r_lst)-1)]
#tr1_like[2:(length(t_r_lst))]-tr1_like[1:(length(t_r_lst)-1)]

# (tr1_like[2:(length(t_r_lst))]-tr1_like[1:(length(t_r_lst)-1)])[(tr1_like[2:(length(t_r_lst))]-tr1_like[1:(length(t_r_lst)-1)])>0]

#(tr2_like[2:(length(t_r_lst))]-tr2_like[1:(length(t_r_lst)-1)])>0



#plik_1e0<-plotly::plot_ly(x =t_r_lst[1:40], y =tr1_like[1:40], name = "tr1_like",type = 'scatter'#, mode = 'lines'
#                         )

#plik_2e0<-plotly::plot_ly(x =t_r_lst[1:80], y =tr2_like[1:80], name = "tr2_like", type = 'scatter'#, mode = 'lines'
 #                        )

#plotly::subplot(plik_1e0, plik_2e0)

```

```{r}


tr_34_ex<-function(H_i){
print(paste(":",H_i))  
tr1_like<-lapply(t_r_lst,function(t_r)cmp_lf_mou(tree_mdf_1e(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()
tr2_like<-lapply(t_r_lst,function(t_r)cmp_lf_mou(tree_mdf_2e(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()

plik_1e<-plot_ly(x =t_r_lst, y =tr1_like, name = "tr1_like",type = 'scatter',mode = 'markers')%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

plik_2e<-plot_ly(x =t_r_lst, y =tr2_like, name = "tr2_like", type = 'scatter',mode = 'markers')%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

#p<-subplot(plik_1e, plik_2e)

return(list(p1=plik_1e,p2=plik_2e))
  
}

rres_34<-tr_34_ex(H_i=2)

rres_34$p1 %>% layout(title =  TeX("\\textbf{Likelihood vs Experiment Eigenvalues in the First Dimension of } \\mathbf H"),
         xaxis = list(title = TeX("\\textbf{Decreasing Rate of } t_{par}")
                      
                     ),
         yaxis = list(title = TeX("\\textbf{Likelihood}")
                     )) %>% config(mathjax = 'cdn')



```





bw 2 and 3

(d) Only increasing tpar or tshr
only increasing

```{r}

#tree_1$tip.label
#tree_1$edge.length
tree_mdf_1ee<-function(tree,N,t_r){  # only increase t_par
  tree_1<-tree
  #tips_egde<-tree_1$edge[tree_1$edge[,2] %in% c(1:100),]
  t_dif<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]*t_r
  tips_edge_length<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]
  tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]<-tips_edge_length+t_dif
 # nontips_edge_length<-tree_1$edge.length[!tree_1$edge[,2] %in% c(1:N)]
 # tree_1$edge.length[!tree_1$edge[,2] %in% c(1:N)]<-nontips_edge_length+sum(t_dif)/length(nontips_edge_length)
  
  return(tree_1)
}

tree_mdf_2ee<-function(tree,N,t_r){   #only increase t_shr
  tree_1<-tree
  #tips_egde<-tree_1$edge[tree_1$edge[,2] %in% c(1:100),]
  
  t_dif<-tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]*t_r
  nontips_edge_length<-tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]
  tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]<-nontips_edge_length+t_dif
 
 # tips_edge_length<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]
#  tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]<-tips_edge_length+sum(t_dif)/length(tips_edge_length)
  
   return(tree_1)
}

```


```{r}
#t_r_lst<-seq(0,0.97,by=0.005)
tr_56<-function(H_i){
print(paste(":",H_i))
t_r_lst_ex<-c(seq(0,1,by=0.005),seq(1.05,3,by=0.05),seq(4,100,by=1),seq(200,10000,by=200))
tr1_like<-lapply(t_r_lst_ex,function(t_r)cmp_lf_mou(tree_mdf_1ee(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()
tr2_like<-lapply(t_r_lst_ex,function(t_r)cmp_lf_mou(tree_mdf_2ee(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()

plik_1e1<-plot_ly(x =t_r_lst_ex, y =tr1_like, name = "tr1_like",type = 'scatter',mode = 'markers')%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

plik_2e1<-plot_ly(x =t_r_lst_ex, y =tr2_like, name = "tr2_like", type = 'scatter',mode = 'markers')%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

p<-subplot(plik_1e1, plik_2e1)

return(list(p=p,tr1_like1=tr1_like,tr2_like2=tr2_like))

}






res_tr_56_lst<-list()
tr56_1_lik_lst<-list()
tr56_2_lik_lst<-list()
for(H_i in c(1:cnt_H)   ){
  res<-tr_56(H_i)
  res_tr_56_lst[[H_i]] <-res$p
  tr56_1_lik_lst[[H_i]] <-res$tr1_like1
  tr56_2_lik_lst[[H_i]] <-res$tr2_like2
}









res_tb1_56<-list()
res_tb2_56<-list()
for(ix in c(1:length(c_sel_al1)) ){
  res_tb1_56[[ix]]<-table((tr56_1_lik_lst[c_sel_al1[ix]][[1]]- r_lm_lst[c_sel_al1[ix]][[1]]$lik)>0)
  res_tb2_56[[ix]]<-table((tr56_2_lik_lst[c_sel_al1[ix]][[1]]- r_lm_lst[c_sel_al1[ix]][[1]]$lik)>0)
  
}

t_r_lst_ex<-c(seq(0,1,by=0.005),seq(1.05,3,by=0.05),seq(4,100,by=1),seq(200,10000,by=200))

ll<-length(t_r_lst_ex)

res_tb1_td_56<-list()
res_tb2_td_56<-list()
for(ix in (c_sel_al1) ){
  res_tb1_td_56[[ix]]<-table( (tr56_1_lik_lst[c_sel_al1[ix]][[1]][c(2:ll)]- tr56_1_lik_lst[c_sel_al1[ix]][[1]][c(1:(ll-1))])>0 )
  res_tb2_td_56[[ix]]<-table((tr56_2_lik_lst[c_sel_al1[ix]][[1]][c(2:ll)]- tr56_2_lik_lst[c_sel_al1[ix]][[1]][c(1:(ll-1))])>0)
  
}





#res_tr_56_lst<-list()
#for(H_i in c_sel_al   ){
#  res_tr_56_lst[[H_i]] <-tr_56(H_i)
#}

#res_tr_56_lst

#tr1_like[2:(length(t_r_lst))]-tr1_like[1:(length(t_r_lst)-1)]
#tr1_like[2:(length(t_r_lst))]-tr1_like[1:(length(t_r_lst)-1)]

# (tr1_like[2:(length(t_r_lst))]-tr1_like[1:(length(t_r_lst)-1)])[(tr1_like[2:(length(t_r_lst))]-tr1_like[1:(length(t_r_lst)-1)])>0]

#(tr2_like[2:(length(t_r_lst))]-tr2_like[1:(length(t_r_lst)-1)])>0



#plik_1e0<-plotly::plot_ly(x =t_r_lst[1:40], y =tr1_like[1:40], name = "tr1_like",type = 'scatter'#, mode = 'lines'
#                         )

#plik_2e0<-plotly::plot_ly(x =t_r_lst[1:80], y =tr2_like[1:80], name = "tr2_like", type = 'scatter'#, mode = 'lines'
 #                        )

#plotly::subplot(plik_1e0, plik_2e0)

```


```{r}


tr_56_ex<-function(H_i){
print(paste(":",H_i))
t_r_lst_ex<-c(seq(0,1,by=0.005),seq(1.05,3,by=0.05),seq(4,100,by=1),seq(200,10000,by=200))
tr1_like<-lapply(t_r_lst_ex,function(t_r)cmp_lf_mou(tree_mdf_1ee(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()
#tr2_like<-lapply(t_r_lst_ex,function(t_r)cmp_lf_mou(tree_mdf_2ee(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()

plik_1e1<-plot_ly(x =t_r_lst_ex, y =tr1_like, name = "tr1_like",type = 'scatter',mode = 'markers')%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

#plik_2e1<-plot_ly(x =t_r_lst_ex, y =tr2_like, name = "tr2_like", type = 'scatter',mode = 'markers')%>%
#   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))

#p<-subplot(plik_1e1, plik_2e1)

return(list(p=plik_1e1))

}


rres_56<-tr_56_ex(H_i=3)

rres_56$p %>% layout(title =  TeX("\\textbf{Likelihood vs Experiment Eigenvalues in the First Dimension of } \\mathbf H"),
         xaxis = list(title = TeX("\\textbf{Increasing Rate of } t_{par}")
                      
                     ),
         yaxis = list(title = TeX("\\textbf{Likelihood}")
                     )) %>% config(mathjax = 'cdn')



```



### 3)


```{r}


tree_mdf_e<-function(tree,N,t_r){  # reduce tip2parent, increase shared length, keep the sum of edge-length unchanged
  tree_1<-tree
  #tips_egde<-tree_1$edge[tree_1$edge[,2] %in% c(1:100),]
 # t_dif1<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]*t_r
  tips_edge_length<-tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]
  tree_1$edge.length[tree_1$edge[,2] %in% c(1:N)]<-tips_edge_length*t_r
  #---------------------------------------------------------------------------
 # t_dif2<-tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]*t_r
  nontips_edge_length<-tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]
  tree_1$edge.length[!(tree_1$edge[,2] %in% c(1:N))]<-nontips_edge_length*t_r
  
  return(tree_1)
}

t_r_lst1<-seq(0.1,100,by=0.1)
#cmp_lf_mou(tree,k,model_MOU,traits)$lik
#cmp_lf_mou(tree_mdf_e(tree,N,t_r=0.1),k,model_MOU,traits)$lik


tr_7<-function(H_i){
  print(paste(":",H_i))
tr_like<-lapply(t_r_lst1,function(t_r)cmp_lf_mou(tree_mdf_e(tree,N,t_r),k,model_MOU_lst[[H_i]],traits_lst[[H_i]])$lik)%>%unlist()
plik_1e<-plot_ly(x =t_r_lst1, y =tr_like, name = "tr1_like",type = 'scatter', mode = 'markers'
                         )%>%
   add_lines(y=r_lm_lst[[H_i]]$lik,name=paste0("lik0"))
#plik_1e

return(list(p=plik_1e,tr_like7=tr_like))
}





res_tr_7_lst<-list()
tr7_lik_lst<-list()
#tr56_2_lik_lst<-list()
for(H_i in (1:cnt_H)   ){
  res<-tr_7(H_i)
  res_tr_7_lst[[H_i]] <-res$p
  tr7_lik_lst[[H_i]] <-res$tr_like7
#  tr56_2_lik_lst[[H_i]] <-res$tr2_like2
}




res_tb1_7<-list()
#res_tb2_56<-list()
for(ix in c(1:length(c_sel_al1)) ){
  res_tb1_7[[ix]]<-table((tr7_lik_lst[c_sel_al1[ix]][[1]]- r_lm_lst[c_sel_al1[ix]][[1]]$lik)>0)
  #res_tb2_56[[ix]]<-table((tr56_2_lik_lst[c_sel_al[ix]][[1]]- r_lm_lst[c_sel_al[ix]][[1]]$lik)>0)
  
}



ll<-length(t_r_lst_ex)

res_tb1_td_7<-list()
#res_tb2_td_56<-list()
for(ix in c(1:length(c_sel_al1)) ){
  res_tb1_td_56[[ix]]<-table((tr56_1_lik_lst[c_sel_al1[ix]][[1]][c(2:ll)]- tr56_1_lik_lst[c_sel_al1[ix]][[1]][c(1:(ll-1))])>0)
  res_tb2_td_56[[ix]]<-table((tr56_2_lik_lst[c_sel_al1[ix]][[1]][c(2:ll)]- tr56_2_lik_lst[c_sel_al1[ix]][[1]][c(1:(ll-1))])>0)
  
}



```



```{r}








res_tr_7_lst[[4]] %>% layout(title =  TeX("\\textbf{Likelihood vs Experiment Eigenvalues in the First Dimension of } \\mathbf H"),
         xaxis = list(title = TeX("\\textbf{Fold of All Length }")
                      
                     ),
         yaxis = list(title = TeX("\\textbf{Likelihood}")
                     )) %>% config(mathjax = 'cdn')



```




---

























