---
title: "04-multiariate OU byR"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(MASS)
```

# Multivariate OU

## 1 Setting
---

If $X \sim N(μ,Σ)$, then from $Y=BX+b => Y \sim N(Bμ+b,BΣB^T)$, 

thus for $X_i  = \mathbf{H}(\Theta - X_i) (t_i - t_{i-1}) + \mathbf{L}\sqrt{t_i - t_{i-1}}W_t+X_{i-1}$, 

$X_i \sim N(\mu',\Sigma')$and  

$\mu' =X_{i-1} +H(\Theta -X_i)(t_{i} -t_{i-1})$

$\Sigma' =L \sqrt{t_i-t_{i-1}}(L \sqrt{t_i-t_{i-1}})^T$

So the form is:

$f^{OU}(X_i|X_{i-1}; \Theta,H,L) = \frac{\mbox{Exp}\left (
-\frac{1}{2}(x_i - \mu')^T \Sigma'^{-1} (x_i - \mu') 
\right)}{\sqrt{(2 \pi)^p|\Sigma'|}}$

then

$ln f^{OU}(X_i|X_{i-1}; \Theta,H,L) =-\frac{1}{2}[(x_i - \mu')^T \Sigma'^{-1} (x_i - \mu')+ln|Σ| +pln(2 \pi)]$

```{r 1.1 }

set.seed(123)
p=2
S =10**3 # steps
p_c=c(10,1.5,0.5)*0.7


Theta = lapply(c(1:p),function(i)p_c[1]*i)%>%unlist()
Theta = Theta%>%as.matrix()
# to generate a positive definite mx
egv_H = lapply(c(1:p),function(i)p_c[2]*i)%>%unlist()

A1 =matrix(rnorm(p*p),nrow=p)*10^2
Q1=qr.Q(qr(A1))
D1 = diag(egv_H)
H = Q1 %*% D1 %*% t(Q1) # #np.linalg.eig(H1)
#eigen(H )

# to generate a L by Cholesky decomposition
egv_L = lapply(c(1:p),function(i)p_c[3]*i)%>%unlist()
set.seed(123)
A2 = matrix(rnorm(p*p),nrow=p)*10^2
A2[upper.tri(A2, diag = FALSE)]=0
L=A2
diag(L)=egv_L

```



```{r 1.2}
ts=seq(0,100,length.out=S)
N=S
dt = ts[2] - ts[1]
X=matrix(0,nrow=N,ncol = p)
X[1,]=rep(1.1, p)

for(i in 1:(N-1)){
  t_x1=X[i,]%>%as.matrix()
  t_x2 = t_x1 + H %*% (Theta- t_x1) * dt  + (L * (dt)**(1/2)) %*% as.matrix(rnorm(p))
  X[i+1,] = as.vector(t_x2)
}



plot(ts, X[,1])
#lines(ts,X[,2],col='green' )
#legend("bottomright", legend=c("acutal temp","predicted temp")
 #        , pch=c(1,1), lty=c(1,1),lwd=c(1,1), col=c("black","red"))


```

## 2.1 Numercial Solution to Optimized Parameter


If $X \sim N(μ,Σ)$, then from $Y=BX+b => Y \sim N(Bμ+b,BΣB^T)$, 

thus for $X_i  = \mathbf{H}(\Theta - X_i) (t_i - t_{i-1}) + \mathbf{L}\sqrt{t_i - t_{i-1}}W_t+X_{i-1}$, 

$X_i \sim N(\mu',\Sigma')$and  

$\mu' =X_{i-1} +H(\Theta -X_i)(t_{i} -t_{i-1})$

$\Sigma' =L \sqrt{t_i-t_{i-1}}(L \sqrt{t_i-t_{i-1}})^T$

So the form is:

$f^{OU}(X_i|X_{i-1}; \Theta,H,L) = \frac{\mbox{Exp}\left (
-\frac{1}{2}(x_i - \mu')^T \Sigma'^{-1} (x_i - \mu') 
\right)}{\sqrt{(2 \pi)^p|\Sigma'|}}$

then

$ln f^{OU}(X_i|X_{i-1}; \Theta,H,L) =-\frac{1}{2}[(x_i - \mu')^T \Sigma'^{-1} (x_i - \mu')+ln|Σ| +pln(2 \pi)]$


```{r 2.1}

Log_OU<-function(X1,X2, dt, p_vars){
	
  #------------------------------------------------------
  Theta_lo=p_vars[1:p]%>%as.matrix()
  
  # to generate a positive definite mx--------------------
  egv_H_lo=p_vars[(p+1):(2*p)]
  D = diag(egv_H_lo)
  H_lo = Q1 %*% D %*% t(Q1)
  
  # to generate a L by Cholesky decomposition
  egv_L_lo = p_vars[(2*p+1):(3*p)]
  #print(egv_L_lo)
  L_lo=A2
  diag(L_lo)=egv_L_lo
  
  #The likelihood--------------------------------------------------  
  X1=X1%>%as.matrix();X2=X2%>%as.matrix() ##....-------
 
  mu2 = X1 + H_lo%*%(Theta_lo-X2)*dt
  #μ₂ = vec(μ₂)
  #t_dif=dt**(0.5)
  Sigma = L_lo%*%t(L_lo)
  Sigma = dt*Sigma
  if(det(Sigma)<1e-08){
    Sigma_inv=ginv(Sigma, tol = sqrt(.Machine$double.eps))
  }else{
     Sigma_inv = solve(Sigma) }
  
 
  
  t1 = X2-mu2
  t2 = log(det(Sigma))
  t3 = p*(log(2*pi))
  #----------------------------
  res = t(t1) %*% Sigma_inv %*% t1 + t2 + t3
  -0.5*res
}

X1=X[4,]
X2=X[5,]
p_vars = c(Theta, egv_H,egv_L)

Log_OU(X1,X2, dt, p_vars)

nllf_OU<-function(X,dt,p_vars){
  lf=c()
  for(i in 2:N){
    X2 = X[i,]
    X1 = X[i-1,]
    lf[i-1] = Log_OU(X1,X2, dt, p_vars)  }
  
  -sum(lf)
  
}

nllf_OU(X,dt,p_vars)

```

```{r optim1}
lower_pv=c(rep(-Inf,p),rep(10^(-8),2*p))
upper_pv=rep(Inf,3*p)


p_vars0=rep(3.6,3*p)
optim(par=p_vars0,fn=nllf_OU,X=X,dt=dt,method="L-BFGS-B",lower=lower_pv)

c(Theta,egv_H,egv_L)
 

```








